% Double spacing, if you want it.
%% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
%% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

%% \maketitle

%% DO NOT include approval page in the submitted PDF!
%% \approvalpage

\copyrightpage


\begin{abstract}
What can machines know about the mind, even theoretically? This dissertation
examines what people (end-users and software engineers) \textit{believe} the
answer to this question might be, where these beliefs come from, and what effect
they have on social behavior and technical practice. First, qualitative and
quantitative data from controlled experiments show how basic biosignals, such as
heartrate, meet with both social context and prior beliefs about the body to
produce mind-related meanings, and affect social decision-making. Second, a
working brain-computer interface probes the diverse beliefs that software
engineers hold about the mind, and uncovers their shared belief that the mind
can and will be read by machines. These cases trace an unstable boundary---one
heavily mediated by human beliefs---between sensing bodies and sensing minds. I
propose the porousness of this boundary as a site for studying the futures of
computer-mediated communication, of security, privacy and surveillance, and of
minds themselves.
\end{abstract}

%% As biosensors creep into smart watches, bands, and ingestibles, they
%% will build increasingly high resolution models of bodies in space. Their ability
%% to divine not just what these bodies do, but what they think and feel, presents
%% an under-explored avenue for understanding and imagining the role these
%% technologies will play in everyday life.


\begin{frontmatter}

\begin{dedication}
\null\vfil
\begin{center}

%% # \begin{flushright}
%% # for the most beautiful mom the world.
%% # we had an amazing, wonderful life together, a life as beautiful and precious as you are.
%% # dad and i carry that life forward everyday, because of the unconditonal love you gave to us,
%% # the greatest, most important gift anyone could ever receive.
%% # the gift you gave to me and dad.
%% # i will always take care of him.
%% # until we see you again.
%% # I love you forever.

%% # also, I have been shaving.
%% # \end{flushright}
To Mom\\\vspace{12pt} I've been shaving (mostly). Thank you for everything. I
love you forever.
\end{center}
\vfil\null
\end{dedication}


\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables

\begin{acknowledgements}
Thank you to John Chuang for being a mentor in every sense of the word, for
accepting me into this ancient model of apprenticeship and showing me how the
work is done. During my time as a PhD student, John assembled BioSENSE, a group
that made my dissertation possible. A few BioSENSors in particular helped me
immensely: Coye Cheshire (with whom I did much of the work in this
dissertation), Richmond Wong, and Noura Howell. Outside of BioSENSE, Alva Noë
raised the relationship between my work and related debates that were hiding in
plain sight. Along the way, Paul Duguid taught me a great deal about what good
scholarship looks like. I would like to thank all of my collaborators, inside
and outside the ISchool, and to thank the ISchool itself for providing me the
freedom and autonomy to pursue a risky topic.

Above all, I would like to thank Mom and Dad, who always believed in the
importance of my work, even when they weren't quite sure what I was doing.

I would also like to thank Chihei Hatakeyama and Hakobune for the peaceful music.
\end{acknowledgements}

%% # Machines will someday read the mind.
%% # I know. But they will.
%% # ``We'' will find a way to make them,
%% # and ``we'' will use any tools at our disposal to do so.

%% # The primary tool we will use is our own interpretation, and theories
%% # of the mind, projecting it onto a physical reality
%% # that is less definite than ``we'' would sometimes like to imagine.

%% # Who is this ``we''?
%% # This dissertation looks primarily (though not exclusively) at software professionals
%% # in the San Francisco Bay Area.

%% # _etc..._

%% # Nick Merrill
%% # Berkeley, California
\end{frontmatter}
